### 2017-01-15 README.Rmd

To demonstrate what visdat looks like when you have different kinds of data, we can use `visdat` to look at the dataset `typical_data`, which is from the excellent [`wakefield package`](https://github.com/trinker/wakefield).

>>>>

To demonstrate what visdat looks like when you have different kinds of data, we can look at the dataset `typical_data`, provided within `visdat`, and created with the excellent [`wakefield` package](https://github.com/trinker/wakefield).
